---
title: 'rapidFFR'
#author: 'HJS'
#date: 'Last update: `r Sys.time()`'
output: html_document
---
```{r, echo=F, warning=F, message=F}
library(knitr)
library(tidyverse)
library(here)
library(broom)
library(ggplot2)
library(gridExtra)
library(car)
library(rstatix)
```

Ignore - Hannah notes  
Files:  
Get SNR, SIG and NZ averaged over both runs from:  
snr_rapidIterations_concat_add  
snr_rapidIterations_concat_sub  
snr_stddIterations_concat_add  
snr_stddIterations_concat_sub

SIG and NZ seperate from each run (calculate z-score?) from:  
signal_mean_rapid_add  
signal_mean_rapid_sub  
nzfloor_mean_rapid_add  
nzfloor_mean_rapid_sub  
signal_mean_std_add  
signal_mean_std_sub  
nzfloor_mean_std_add  
nzfloor_mean_std_sub  

## Exp 1: standard vs. rapid  
```{r, 'exp1_load_data', echo=F, message=F}
setwd("/Volumes/UCL_DR_HJS/projects/rapidFFR/1_data/4_analysis/")

#std_add <- read.csv("out/Experiment1_normalVrapid/snr_stdIterations_concat_add.csv", header=T)
#std_sub <- read.csv("out/Experiment1_normalVrapid/snr_stdIterations_concat_sub.csv", header=T)

rapid_add <- read.csv("out/Experiment1_normalVrapid/snr_rapidIterations_concat_add.csv", header=T)
rapid_sub <- read.csv("out/Experiment1_normalVrapid/snr_rapidIterations_concat_sub.csv", header=T)

#head(rapid_add)
#head(rapid_sub)

rapid_add_F1 <- subset(rapid_add,var_name=="Freq1")
rapid_add_F2 <- subset(rapid_add,var_name=="Freq2")
rapid_add_F3 <- subset(rapid_add,var_name=="Freq3")
rapid_sub_F4 <- subset(rapid_sub,var_name=="Freq4")
rapid_sub_F5 <- subset(rapid_sub,var_name=="Freq5")

std_add_chunk <- read.csv("out/Experiment1_normalVrapid/snr_stdChunks_concat_add.csv", header=T)
std_sub_chunk <- read.csv("out/Experiment1_normalVrapid/snr_stdChunks_concat_sub.csv", header=T)

#head(std_add_chunk)
#head(std_sub_chunk)

std_add_chunk_F1 <- subset(std_add_chunk,var_name=="Freq1")
std_add_chunk_F2 <- subset(std_add_chunk,var_name=="Freq2")
std_add_chunk_F3 <- subset(std_add_chunk,var_name=="Freq3")
std_sub_chunk_F4 <- subset(std_sub_chunk,var_name=="Freq4")
std_sub_chunk_F5 <- subset(std_sub_chunk,var_name=="Freq5")

#std_add <- read.csv("out/Experiment1_normalVrapid/snr_stdIterations_concat_add.csv", header=T)
#std_sub <- read.csv("out/Experiment1_normalVrapid/snr_stdIterations_concat_sub.csv", header=T)

#head(std_add)
#head(std_sub)

#std_add_F1 <- subset(std_add,var_name=="Freq1")
#std_add_F2 <- subset(std_add,var_name=="Freq2")
#std_add_F3 <- subset(std_add,var_name=="Freq3")
#std_sub_F4 <- subset(std_sub,var_name=="Freq4")
#std_sub_F5 <- subset(std_sub,var_name=="Freq5")
```
### Quality of data
**Figure 1**:  
Schematic of standard, rapid and longRapid FFR. Showing what chunks/iterations etc. and common timings are.

**Figure 2**:  
2x2 panel  
top left: eeg std in red  
top right: eeg rapid in blue  
bottom left: Power std in red (showing harmonics)  
bottom right: Power rapid in blue (showing harmonics)  
*Caption*: Grand averaged time course and spectra representations of EEG recorded FFRs for standard (red) and rapid (blue) presentations. EEG data extracted from ... electrodes....


### Q1: Is the signal sig. different from the noise?

**Figure 3 option 1**:  
```{r, Figure3: Option 1, echo=F, message=F, warning=F}
ymin = -5
ymax = 25

#summary(std_add_chunk_F1)

####################
### standard chunks

fig3Aa_std <- ggplot(std_add_chunk_F1, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="red") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("F0+") + ylab("SNR") + ylim(ymin, ymax)
#fig3Aa_std

fig3Ab_std <- ggplot(std_add_chunk_F2, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="red") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H2+") + ylab("SNR") + ylim(ymin, ymax)

fig3Ac_std <- ggplot(std_add_chunk_F3, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="red") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H3+") + ylab("SNR") + ylim(ymin, ymax)

fig3Ad_std <- ggplot(std_sub_chunk_F4, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="red") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H4-") + ylab("SNR") + ylim(ymin, ymax)

fig3Ae_std <- ggplot(std_sub_chunk_F5, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="red") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H5-") + ylab("SNR") + ylim(ymin, ymax)

grid.arrange(fig3Aa_std, fig3Ab_std, fig3Ac_std, fig3Ad_std, fig3Ae_std, nrow=2)

####################
### rapid iterations

fig3Aa <- ggplot(rapid_add_F1, aes(x=iteration, y=snr, group=iteration)) + 
  geom_boxplot(color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("F0+") + ylab("SNR") + ylim(ymin, ymax)
#fig3Aa

fig3Ab <- ggplot(rapid_add_F2, aes(x=iteration, y=snr, group=iteration)) + 
  geom_boxplot(color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H2+") + ylab("SNR") + ylim(ymin, ymax)

fig3Ac <- ggplot(rapid_add_F3, aes(x=iteration, y=snr, group=iteration)) + 
  geom_boxplot(color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H3+") + ylab("SNR") + ylim(ymin, ymax)

fig3Ad <- ggplot(rapid_sub_F4, aes(x=iteration, y=snr, group=iteration)) + 
  geom_boxplot(color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H4-") + ylab("SNR") + ylim(ymin, ymax)

fig3Ae <- ggplot(rapid_sub_F5, aes(x=iteration, y=snr, group=iteration)) + 
  geom_boxplot(color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H5-") + ylab("SNR") + ylim(ymin, ymax)

grid.arrange(fig3Aa, fig3Ab, fig3Ac, fig3Ad, fig3Ae, nrow=2)
```

**Stats**:  
$\color{red}{\text{Q}}$: One-sample t-test for SNR to 0? Nope!  
$\color{red}{\text{Q}}$: ANOVA 1 (SNR) x 15 (iterations) - done. But this looks at the change across iterations rather than if signal is above noise.  
$\color{red}{\text{Q}}$: ANOVA 1 (snr) x 2 (std, rapid). To compare std to rapid at common iterations (1500, 3000, 4500, 6000, 7500?  
$\color{red}{\text{Q}}$: No stats here and do them on Figure 3: Option 2 data instead  

```{r, Figure3: Option 1 stats, echo=F, message=F, warning=F, results='hide'}
#summary(rapid_add_F1)

# F0
# check homogeneity
leveneTest(snr ~ as.factor(iteration), data = rapid_add_F1)
# compute the analysis of variance
snr.iterations_F1 <- aov(snr ~ as.factor(iteration), data = rapid_add_F1)
# summary of the analysis
summary(snr.iterations_F1)
# posthocs
#TukeyHSD(snr.iterations)

# H2
# check homogeneity
leveneTest(snr ~ as.factor(iteration), data = rapid_add_F2)
# compute the analysis of variance
snr.iterations.F2 <- aov(snr ~ as.factor(iteration), data = rapid_add_F2)
# summary of the analysis
summary(snr.iterations.F2)
# posthocs
#TukeyHSD(snr.iterations.F2)

# H3
# check homogeneity
leveneTest(snr ~ as.factor(iteration), data = rapid_add_F3)
# compute the analysis of variance
snr.iterations.F3 <- aov(snr ~ as.factor(iteration), data = rapid_add_F3)
# summary of the analysis
summary(snr.iterations.F3)
# posthocs
#TukeyHSD(snr.iterations.F3)

# H4
# check homogeneity
leveneTest(snr ~ as.factor(iteration), data = rapid_sub_F4)
# compute the analysis of variance
snr.iterations.F4 <- aov(snr ~ as.factor(iteration), data = rapid_sub_F4)
# summary of the analysis
summary(snr.iterations.F4)
# posthocs
#TukeyHSD(snr.iterations.F4)

# H5
# check homogeneity
leveneTest(snr ~ as.factor(iteration), data = rapid_sub_F5)
# compute the analysis of variance
snr.iterations.F5 <- aov(snr ~ as.factor(iteration), data = rapid_sub_F5)
# summary of the analysis
summary(snr.iterations.F5)
# posthocs
#TukeyHSD(snr.iterations.F5)

```

ANOVA 1 (SNR) x 15 (iterations):  
- F0+ sig. effect of iterations  
- H2+ sig. effect of iterations  
- H3+ NO sig. effect of iterations  
- H4- NO sig. effect of iterations  
- H5- sig. effect of iterations  

**Figure 3 option 2**:  
```{r, Figure3: Option 2, echo=F, message=F, warning=F}
ymin = 0
ymax = 0.4

####################
### standard chunks

fig3Ba_std <- ggplot(std_add_chunk_F1, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="red", fill="red") +
  geom_boxplot(aes(y = meanSIG), color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("F0+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)
#fig3Ba_std

fig3Bb_std <- ggplot(std_add_chunk_F2, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="red", fill="red") +
  geom_boxplot(aes(y = meanSIG), color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H2+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)

fig3Bc_std <- ggplot(std_add_chunk_F3, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="red", fill="red") +
  geom_boxplot(aes(y = meanSIG), color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H3+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)

fig3Bd_std <- ggplot(std_sub_chunk_F4, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="red", fill="red") +
  geom_boxplot(aes(y = meanSIG), color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H4-") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)

fig3Be_std <- ggplot(std_sub_chunk_F5, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="red", fill="red") +
  geom_boxplot(aes(y = meanSIG), color="red") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H5-") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)

grid.arrange(fig3Ba_std, fig3Bb_std, fig3Bc_std, fig3Bd_std, fig3Be_std, nrow=2)

####################
### rapid iterations

fig3Ba <- ggplot(rapid_add_F1, aes(x=iteration, group=iteration)) + 
  geom_boxplot(aes(y = meanNZ), color="blue", fill="blue") +
  geom_boxplot(aes(y = meanSIG), color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("F0+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, ymax)
#fig3Ba

fig3Bb <- ggplot(rapid_add_F2, aes(x=iteration, group=iteration)) + 
  geom_boxplot(aes(y = meanNZ), color="blue", fill="blue") +
  geom_boxplot(aes(y = meanSIG), color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H2+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.3)

fig3Bc <- ggplot(rapid_add_F3, aes(x=iteration, group=iteration)) + 
  geom_boxplot(aes(y = meanNZ), color="blue", fill="blue") +
  geom_boxplot(aes(y = meanSIG), color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H3+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.15)

fig3Bd <- ggplot(rapid_sub_F4, aes(x=iteration, group=iteration)) + 
  geom_boxplot(aes(y = meanNZ), color="blue", fill="blue") +
  geom_boxplot(aes(y = meanSIG), color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H4-") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)

fig3Be <- ggplot(rapid_sub_F5, aes(x=iteration, group=iteration)) + 
  geom_boxplot(aes(y = meanNZ), color="blue", fill="blue") +
  geom_boxplot(aes(y = meanSIG), color="blue") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H5-") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)

grid.arrange(fig3Ba, fig3Bb, fig3Bc, fig3Bd, fig3Be, nrow=2)
```

**Stats**:  
$\color{red}{\text{Q}}$: ANOVA 2 (signal, noise) x 15 (iterations). Does the difference between signal and noise changes across iterations.  
$\color{red}{\text{Q}}$: ANOVA 2 (signal, noise) x 2 (std, rapid). To compare std to rapid at common iterations (1500, 3000, 4500, 6000, 7500?  

```{r, Figure3: Option 2 stats, echo=F, message=F, warning=F, results='hide'}
# need std to run
```


**Figure 4**:  
two graphs: add on left and sub on right  
- red = standard  
- blue = rapid  
- y axis: amplitude ($\mu$V peak)  
- x axis: F0 H2 H3 H4 H5

```{r, Figure4, echo=F, message=F, warning=F, results='hide'}
ymin = 0
ymax = 0.4

summary(rapid_add)
rapid_add$iteration <- as.factor(rapid_add$iteration)
summary(rapid_add)

rapid_add_select1500 <- subset(rapid_add, iteration=="1500")
rapid_add_select3000 <- subset(rapid_add, iteration=="3000")
rapid_add_select4500 <- subset(rapid_add, iteration=="4500")
rapid_add_select6000 <- subset(rapid_add, iteration=="6000")
rapid_add_select7500 <- subset(rapid_add, iteration=="7500")

rapid_add_select <- rbind(rapid_add_select1500, rapid_add_select3000, rapid_add_select4500, rapid_add_select6000, rapid_add_select7500)

summary(rapid_add_select)
head(rapid_add_select)

#add_select <- rbind(rapid_add_select, std_add) # need std_add to work!

# add
#fig4a <- ggplot(rapid_add, aes(x=var_name, y = meanSIG, group=condition)) + 
#  geom_boxplot() +
#  scale_color_manual(values=c("#blue", "#red")) +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
#  theme_classic() +
#  ggtitle("Addition") + ylab(expression("mean signal amplitude"~"("*mu*V*")")) + ylim(ymin, ymax)
#fig4a

summary(rapid_sub)
rapid_sub$iteration <- as.factor(rapid_sub$iteration)
summary(rapid_sub)

rapid_sub_select1500 <- subset(rapid_sub, iteration=="1500")
rapid_sub_select3000 <- subset(rapid_sub, iteration=="3000")
rapid_sub_select4500 <- subset(rapid_sub, iteration=="4500")
rapid_sub_select6000 <- subset(rapid_sub, iteration=="6000")
rapid_sub_select7500 <- subset(rapid_sub, iteration=="7500")

rapid_sub_select <- rbind(rapid_sub_select1500, rapid_sub_select3000, rapid_sub_select4500, rapid_sub_select6000, rapid_sub_select7500)

summary(rapid_sub_select)
head(rapid_sub_select)

#sub_select <- rbind(rapid_sub_select, std_sub) # need std_sub to work!

# sub
#fig4b <- ggplot(rapid_sub, aes(x=var_name, y = meanSIG, group=condition)) + 
#  geom_boxplot() +
#  scale_color_manual(values=c("#blue", "#red")) +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
#  theme_classic() +
#  ggtitle("Subtraction") + ylab(expression("mean signal amplitude"~"("*mu*V*")")) + ylim(ymin, ymax)
#fig4b

#grid.arrange(fig4a, fig4b, nrow=1)
```
**Stats**:  
$\color{red}{\text{Q}}$: ANOVA 2 (std, rapid) x 5 (harmonics). This looks at if peak mag. is different between standard and rapid FFR across harmonics  

**Figure 5**:  
correlations scatters for amplitude ($\mu$V peak) 
seperate plots for F1, F2, F3 etc.  
- grey scatter  
- black correlation line  
- y axis: rapid  
- x axis: standard  
$\color{red}{\text{Q}}$: which iteration should we use? 4500??
$\color{red}{\text{Q}}$: want z-score of run 1 v run 2?


### Q2: How long should the rapid FFR be?
$\color{red}{\text{Q}}$: fit at 63%?

## Exp 2: long rapid
### Q3: How does the signal and noise change over a 9 min recording?
```{r, 'exp2_load_data', echo=F, message=F}
setwd("/Volumes/UCL_DR_HJS/projects/rapidFFR/1_data/4_analysis/")

longRapid_add <- read.csv("out/Experiment2_longRapid/snr_longRapid_concat_add.csv", header=T)
longRapid_sub <- read.csv("out/Experiment2_longRapid/snr_longRapid_concat_sub.csv", header=T)

# head(longRapid_add)
# head(longRapid_sub)

longRapid_add_F1 <- subset(longRapid_add,var_name=="Freq1")
longRapid_add_F2 <- subset(longRapid_add,var_name=="Freq2")
longRapid_add_F3 <- subset(longRapid_add,var_name=="Freq3")
longRapid_sub_F4 <- subset(longRapid_sub,var_name=="Freq4")
longRapid_sub_F5 <- subset(longRapid_sub,var_name=="Freq5")

```

**Figure 6 option 1**:  
```{r, Figure6: Option 1, echo=F, message=F, warning=F}
ymin = -5
ymax = 25

summary(longRapid_add_F1)

fig6Aa <- ggplot(longRapid_add_F1, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("F0+") + ylab("SNR") + ylim(ymin, ymax)
#fig6Aa

fig6Ab <- ggplot(longRapid_add_F2, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H2+") + ylab("SNR") + ylim(ymin, ymax)

fig6Ac <- ggplot(longRapid_add_F3, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H3+") + ylab("SNR") + ylim(ymin, ymax)

fig6Ad <- ggplot(longRapid_sub_F4, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H4-") + ylab("SNR") + ylim(ymin, ymax)

fig6Ae <- ggplot(longRapid_sub_F5, aes(x=chunk, y=snr, group=chunk)) + 
  geom_boxplot(color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="blue") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H5-") + ylab("SNR") + ylim(ymin, ymax)

grid.arrange(fig6Aa, fig6Ab, fig6Ac, fig6Ad, fig6Ae, nrow=2)
```

**Stats**:  
Option 1:  
ANOVA 1 (snr) x 15 (chunks). Does snr change across chunks for each component?
```{r, Figure6: Option 1 anova, echo=F, message=F, warning=F, results='hide'}
#summary(longRapid_add_F1)

# F0
# check homogeneity
leveneTest(snr ~ as.factor(chunk), data = longRapid_add_F1)
# compute the analysis of variance
snr.chunks_F1 <- aov(snr ~ as.factor(chunk), data = longRapid_add_F1)
# summary of the analysis
summary(snr.chunks_F1)
# posthocs
#TukeyHSD(snr.chunks_F1)

# H2
# check homogeneity
leveneTest(snr ~ as.factor(chunk), data = longRapid_add_F2)
# compute the analysis of variance
snr.chunks_F2 <- aov(snr ~ as.factor(chunk), data = longRapid_add_F2)
# summary of the analysis
summary(snr.chunks_F2)
# posthocs
#TukeyHSD(snr.chunks_F2)

# H3
# check homogeneity
leveneTest(snr ~ as.factor(chunk), data = longRapid_add_F3)
# compute the analysis of variance
snr.chunks_F3 <- aov(snr ~ as.factor(chunk), data = longRapid_add_F3)
# summary of the analysis
summary(snr.chunks_F3)
# posthocs
#TukeyHSD(snr.chunks_F3)

# H4
# check homogeneity
leveneTest(snr ~ as.factor(chunk), data = longRapid_sub_F4)
# compute the analysis of variance
snr.chunks_F4 <- aov(snr ~ as.factor(chunk), data = longRapid_sub_F4)
# summary of the analysis
summary(snr.chunks_F4)
# posthocs
#TukeyHSD(snr.chunks_F4)

# H5
# check homogeneity
leveneTest(snr ~ as.factor(chunk), data = longRapid_sub_F5)
# compute the analysis of variance
snr.chunks_F5 <- aov(snr ~ as.factor(chunk), data = longRapid_sub_F5)
# summary of the analysis
summary(snr.chunks_F5)
# posthocs
#TukeyHSD(snr.chunks_F5)

```

Regression: Does snr change across chunks for each component?
```{r, Figure6: Option 1 regression, echo=F, message=F, warning=F, results='hide'}
# F0
lmSNR_F1 <- lm(snr ~ chunk, data = longRapid_add_F1)
summary(lmSNR_F1)
lmSNR_F1plot <- plot(lmSNR_F1$residuals, pch = 16, col = "purple")

# F2
lmSNR_F2 <- lm(snr ~ chunk, data = longRapid_add_F2)
summary(lmSNR_F2)
lmSNR_F2plot <- plot(lmSNR_F2$residuals, pch = 16, col = "purple")

# F3
lmSNR_F3 <- lm(snr ~ chunk, data = longRapid_add_F3)
summary(lmSNR_F3)
lmSNR_F3plot <- plot(lmSNR_F3$residuals, pch = 16, col = "purple")

# F4
lmSNR_F4 <- lm(snr ~ chunk, data = longRapid_sub_F4)
summary(lmSNR_F4)
lmSNR_F4plot <- plot(lmSNR_F4$residuals, pch = 16, col = "purple")

# F5
lmSNR_F5 <- lm(snr ~ chunk, data = longRapid_sub_F5)
summary(lmSNR_F5)
lmSNR_F5plot <- plot(lmSNR_F5$residuals, pch = 16, col = "purple")

lmSNR_F1plot


grid.arrange(plot(lmSNR_F1$residuals, pch = 16, col = "red"), plot(lmSNR_F2$residuals, pch = 16, col = "orange"), plot(lmSNR_F3$residuals, pch = 16, col = "green"), plot(lmSNR_F4$residuals, pch = 16, col = "blue"), plot(lmSNR_F5$residuals, pch = 16, col = "purple"), nrow=2)

```

- F0+ NO sig. effect of chunks  
- H2+ NO sig. effect of chunks   
- H3+ NO sig. effect of chunks    
- H4- NO sig. effect of chunks    
- H5- NO sig. effect of chunks   
=> SNR does not significantly change over the 9 mins recording for any of the harmonics.

**Figure 6 option 2**:  
```{r, Figure6: Option 2, echo=F, message=F, warning=F}
ymin = 0
ymax = 0.4

fig6Ba <- ggplot(longRapid_add_F1, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="purple", fill="purple") +
  geom_boxplot(aes(y = meanSIG), color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="purple") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("F0+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, ymax)
#fig6Ba

fig6Bb <- ggplot(longRapid_add_F2, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="purple", fill="purple") +
  geom_boxplot(aes(y = meanSIG), color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="purple") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H2+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.3)

fig6Bc <- ggplot(longRapid_add_F3, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="purple", fill="purple") +
  geom_boxplot(aes(y = meanSIG), color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="purple") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H3+") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.15)

fig6Bd <- ggplot(longRapid_sub_F4, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="purple", fill="purple") +
  geom_boxplot(aes(y = meanSIG), color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="purple") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H4-") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)

fig6Be <- ggplot(longRapid_sub_F5, aes(x=chunk, group=chunk)) + 
  geom_boxplot(aes(y = meanNZ), color="purple", fill="purple") +
  geom_boxplot(aes(y = meanSIG), color="purple") +
  #geom_dotplot(binaxis='y', stackdir='center', dotsize=0.3, color="purple") +
  #geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_classic() +
  ggtitle("H5-") + ylab(expression("amplitude"~"("*mu*V*")")) + ylim(ymin, 0.05)

grid.arrange(fig6Ba, fig6Bb, fig6Bc, fig6Bd, fig6Be, nrow=2)
```

**Stats**:  
Option 2:  
$\color{red}{\text{Q}}$: How do you do a 2 (signal, noise) x 15 (chunk) ANOVA in r!?  

ANOVA 1 (signal) x 15 (chunks). Does the signal change across chunks?  

```{r, Figure6: Option 2 statsA, echo=F, message=F, warning=F, results='hide'}
#summary(longRapid_add_F1)

# F0
# check homogeneity
leveneTest(meanSIG ~ as.factor(chunk), data = longRapid_add_F1)
# compute the analysis of variance
meanSIG.chunks_F1 <- aov(meanSIG ~ as.factor(chunk), data = longRapid_add_F1)
# summary of the analysis
summary(meanSIG.chunks_F1)

# H2
# check homogeneity
leveneTest(meanSIG ~ as.factor(chunk), data = longRapid_add_F2)
# compute the analysis of variance
meanSIG.chunks_F2 <- aov(meanSIG ~ as.factor(chunk), data = longRapid_add_F2)
# summary of the analysis
summary(meanSIG.chunks_F2)

# H3
# check homogeneity
leveneTest(meanSIG ~ as.factor(chunk), data = longRapid_add_F3)
# compute the analysis of variance
meanSIG.chunks_F3 <- aov(meanSIG ~ as.factor(chunk), data = longRapid_add_F3)
# summary of the analysis
summary(meanSIG.chunks_F3)

# H4
# check homogeneity
leveneTest(meanSIG ~ as.factor(chunk), data = longRapid_sub_F4)
# compute the analysis of variance
meanSIG.chunks_F4 <- aov(meanSIG ~ as.factor(chunk), data = longRapid_sub_F4)
# summary of the analysis
summary(meanSIG.chunks_F4)

# H5
# check homogeneity
leveneTest(meanSIG ~ as.factor(chunk), data = longRapid_sub_F5)
# compute the analysis of variance
meanSIG.chunks_F5 <- aov(meanSIG ~ as.factor(chunk), data = longRapid_sub_F5)
# summary of the analysis
summary(meanSIG.chunks_F5)
```

- F0+ NO sig. effect of chunks  
- H2+ NO sig. effect of chunks   
- H3+ NO sig. effect of chunks    
- H4- NO sig. effect of chunks    
- H5- NO sig. effect of chunks   
=> mean signal does not significantly change over the 9 mins recording for any of the harmonics.


ANOVA 1 (noise) x 15 (chunks). Does the noise change across chunks?  

```{r, Figure6: Option 2 statsB, echo=F, message=F, warning=F, results='hide'}
#summary(longRapid_add_F1)

# F0
# check homogeneity
leveneTest(meanNZ ~ as.factor(chunk), data = longRapid_add_F1)
# compute the analysis of variance
meanNZ.chunks_F1 <- aov(meanNZ ~ as.factor(chunk), data = longRapid_add_F1)
# summary of the analysis
summary(meanNZ.chunks_F1)

# H2
# check homogeneity
leveneTest(meanNZ ~ as.factor(chunk), data = longRapid_add_F2)
# compute the analysis of variance
meanNZ.chunks_F2 <- aov(meanNZ ~ as.factor(chunk), data = longRapid_add_F2)
# summary of the analysis
summary(meanNZ.chunks_F2)

# H3
# check homogeneity
leveneTest(meanNZ ~ as.factor(chunk), data = longRapid_add_F3)
# compute the analysis of variance
meanNZ.chunks_F3 <- aov(meanNZ ~ as.factor(chunk), data = longRapid_add_F3)
# summary of the analysis
summary(meanNZ.chunks_F3)

# H4
# check homogeneity
leveneTest(meanNZ ~ as.factor(chunk), data = longRapid_sub_F4)
# compute the analysis of variance
meanNZ.chunks_F4 <- aov(meanNZ ~ as.factor(chunk), data = longRapid_sub_F4)
# summary of the analysis
summary(meanNZ.chunks_F4)

# H5
# check homogeneity
leveneTest(meanNZ ~ as.factor(chunk), data = longRapid_sub_F5)
# compute the analysis of variance
meanNZ.chunks_F5 <- aov(meanNZ ~ as.factor(chunk), data = longRapid_sub_F5)
# summary of the analysis
summary(meanNZ.chunks_F5)
```

- F0+ NO sig. effect of chunks  
- H2+ NO sig. effect of chunks   
- H3+ NO sig. effect of chunks    
- H4- NO sig. effect of chunks    
- H5- NO sig. effect of chunks   
=> mean noise does not significantly change over the 9 mins recording for any of the harmonics.


```{r, Figure6: Option 2 statsC, echo=F, message=F, warning=F, results='hide'}
#summary(longRapid_add_F1)
#MANOVA
res.man <- manova(cbind(meanNZ, meanSIG) ~ chunk, data = longRapid_add_F1)
summary(res.man)
summary.aov(res.man)
```